% This is sigproc-sp.tex -FILE FOR V2.6SP OF ACM_PROC_ARTICLE-SP.CLS
% OCTOBER 2002
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V2.6SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.6SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
%
%  However, both the CopyrightYear (default to 2002) and the ACM Copyright Data
% (default to X-XXXXX-XX-X/XX/XX) can still be over-ridden by whatever the author
% inserts into the source .tex file.
% e.g.
% \CopyrightYear{2003} will cause 2003 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@acm.org 
%
% For tracking purposes - this is V2.6SP - OCTOBER 2002


\documentclass[12pt]{article}

\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setlength{\parindent}{0in} 

\usepackage{graphicx} %For jpg figure inclusion
\usepackage{times} %For typeface
\usepackage{epsfig}
\usepackage{color} %For Comments
%\usepackage[all]{xy}
\usepackage{float}
%\usepackage{subfigure} 
\usepackage{hyperref}
\usepackage{url}
\usepackage{parskip}

%% Elena's favorite green (thanks, Fernando!)
\definecolor{ForestGreen}{RGB}{34,139,34}
% Uncomment this if you want to show work-in-progress comments
%\newcommand{\comment}[1]{{\bf \tt  {#1}}}
% Uncomment this if you don't want to show comments
\newcommand{\comment}[1]{}
\newcommand{\emcomment}[1]{\textcolor{ForestGreen}{\comment{Elena: {#1}}}}
\newcommand{\todo}[1]{\textcolor{blue}{\comment{To Do: {#1}}}}

\newcommand{\pscomment}[1]{\textcolor{red}{\comment{Paul: {#1}}}}
\newcommand{\mmcomment}[1]{\textcolor{magenta}{\comment{Max: {#1}}}}
\begin{document}
\pagestyle{plain}
%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\setpagenumber{50}
%\CopyrightYear{2002} % Allows default copyright year (2002) to be
%over-ridden - IF NEED BE. 
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data
%(X-XXXXX-XX-X/XX/XX) to be over-ridden. 
% --- End of Author Metadata ---

\title{Clojure User Scenarios}
%\subtitle{[Extended Abstract \comment{DO WE NEED THIS?}]
%\titlenote{}}
%
% You need the command \numberofauthors to handle the "boxing"
% and alignment of the authors under the title, and to add
% a section for authors number 4 through n.
%
% Up to the first three authors are aligned under the title;
% use the \alignauthor commands below to handle those names
% and affiliations. Add names, affiliations, addresses for
% additional authors as the argument to \additionalauthors;
% these will be set for you without further effort on your
% part as the last section in the body of your article BEFORE
% References or any Appendices.

\author{
Paul Schliep and Aaron Lemmon \\
Computer Science Discipline \\
University of Minnesota Morris\\
Morris, MN 56267\\
schli202@umn.edu, lemmo031@umn.edu
}

\date{}

\maketitle
\thispagestyle{empty}




\newpage
\setcounter{page}{1}

\section{Day 1}
Suzie starts her first “Hello World” program on the first day of class in a repl from our project. Here are all her code attempts:

\begin{verbatim}
	print(Hello World)
\end{verbatim}
\begin{itemize}
	\item This breaks because clojure thinks that Hello is a symbol (identifier) when Suzie wanted it to be just plain text. Our program could respond with a suggestion that if the user wanted the phrase to be plain text to surround it with double quotes. It could also suggest to double-check that the user spelled the symbol correctly. 
\end{itemize}

\begin{verbatim}
	print(“Hello World”)
\end{verbatim}
\begin{itemize}
	\item This breaks because Clojure thinks the first thing after an open paren should be a function. Our program could respond with a suggestion to the user to make sure that the item right after the open paren is a function, otherwise check syntax. 
\end{itemize}

\begin{verbatim}
	(print Hello World)
\end{verbatim}
\begin{itemize}
	\item This is the same scenario as the first.
\end{itemize}

\begin{verbatim}
	(print "Hello World")
\end{verbatim}
\begin{itemize}
	\item This works!
\end{itemize}

\section{Day 2}
For the second day, Jaden wants to define a function in a repl from within our project. Here are all his code attempts:

\begin{verbatim}
	(fn squareThis input*input)
\end{verbatim}
\begin{itemize}
	\item WRONG, and we don’t know why or how to help.
\end{itemize}

\begin{verbatim}
	(fn squareThis [x] (* x x)))
	(squareThis 5)max
\end{verbatim}
\begin{itemize}
	\item Unable to resolve symbol “squareThis”. This breaks because fn doesn’t make the function last like defn does. fn is only temporary. Our program suggest that the user makes sure he/she defined the symbol correctly.
\end{itemize}

\begin{verbatim}
	(defn squareThis [x] (* x x))
\end{verbatim}
\begin{itemize}
	\item This works!
\end{itemize}

\section{Day 3}
On the third day of Clojure, Laken is super-excited to start working with lists! She has a list of her favorite bands and she wants to add a new one. Here are her attempts to do this in Clojure:
\begin{verbatim}
	(conj "ACDC" ("Daft Punk" "U2" "ZZ Top"))
\end{verbatim}
\begin{itemize}
	\item This breaks because there is no single quote on the parentheses, so Clojure thinks that the first thing after the open paren is a function, but a string was provided instead. Our program could suggest to the user if they are trying to use lists, to put a single quote before the open paren. 
\end{itemize}

\begin{verbatim}
	(conj "ACDC" ‘("Daft Punk" "U2" "ZZ Top"))
\end{verbatim}
\begin{itemize}
	\item This breaks because the arguments conj are in the wrong order. When class cast exceptions like these are thrown our program could suggest double-checking the correct order of arguments.
\end{itemize}

\begin{verbatim}
	(conj ‘("Daft Punk" "U2" "ZZ Top") "ACDC")
\end{verbatim}
\begin{itemize}
	\item This works!
\end{itemize}

\section{Day 4}
On the fourth day of Clojure, Keylan is a little bit nervous to work with Maps. He wants to update a value associated with a key in a map he has created. Here are his attempts:
\begin{verbatim}
	(assoc :a 3 {:a 5, :b 8, :c 9})
\end{verbatim}
\begin{itemize}
	\item This breaks because Clojure is trying to apply assoc to :a where it expects a collection to update. So, our program could suggest to the user to make sure their arguments are in the right order.
\end{itemize}

\begin{verbatim}
	(assoc (:a 3) {:a 5, :b 8, :c 9})
\end{verbatim}
\begin{itemize}
	\item This breaks because Clojure detects that the wrong number of arguments were passed to the function. assoc expects an odd number of arguments but only 2 were passed in. Our program can tell the user to double-check the function definition to see how many arguments it expects.
\end{itemize}

\begin{verbatim}
	(assoc {:a 3} {:a 5, :b 8, :c 9})
\end{verbatim}
\begin{itemize}
	\item This breaks for the same reason as above
\end{itemize}

\begin{verbatim}
	(assoc {:a 5, :b 8, :c 9} :a 3)
\end{verbatim}
\begin{itemize}
	\item This works!
\end{itemize}

\section{Day 5}
On the fifth day of Clojure, Addison needs to write a function which takes a sequence and returns the maximum value from the sequence without using max or key-max. Here are Addison's attempts:

\begin{verbatim}
	(defn [coll] penultimate (last (drop-last coll)))
\end{verbatim}
\begin{itemize}
	\item This throws an IllegalArgumentException: Don't know how to create ISeq from: clojure.lang.Symbol. In this specific case we could give a hint that the function name and the parameter list are out of order.
\end{itemize}

\begin{verbatim}
	(defn penultimate [coll] (last (drop-last coll)))
\end{verbatim}
\begin{itemize}
	\item This works!
\end{itemize}

% That's all folks!
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
